manuscript_notes

### 2024-12-10 notes/manuscript_notes.Rmd
update ms-notes.

- check legends of all Figures, and add more info if needed

@@

- add info on simulation and power analysis (section 4.4 + summary in section 4)

- delete code in Tutorial_2a about brand new hypothetical subject?

- use timebin or time bins?

- use multi-level or multilevel ?

@@

-> Done. !!!!! delete one....

@@

# Sven dec 10

@@

Mention tut 2b priors...   todo

Section 4... comments?

appendices/separate Rmd file...

clean up html of Rmd files

>>>>

- check legends of all Figures, and add more info if needed -> Done

@@

- add info on simulation and power analysis (section 4.4 + summary in section 4). Done.

- delete code in Tutorial_2a about brand new hypothetical subject? Done.

- use timebin or time bins? Timebin.

- use multi-level or multilevel ? Multilevel.

@@

@@

# Sven dec 10 still to do:

@@

appendix/separate Rmd file... + {var} in functions...?

clean up html files (delete old figures, Mention tut 2b priors, ...)

change Figure comparison for ca

check for timebin, multilevel
